---
title: 'ggplot2: Themes'
date: '2016-06-25'
slug: ggplot2-themes
topics:
  - ggplot2
tags:
  - ggplot2
  - visualization
draft: yes
---

This is the last post in the series **Elegant Data Visualization with ggplot2**. In the previous [post](https://rsquaredacademy.github.io/blog/post/ggplot2-facets-combine-multiple-plots/), we learnt to combine multiple plots. In this post, we will learn about themes.

```{r facet, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
```

## Classic Dark on Light

```{r facet1}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_bw()
```

## Default Gray

```{r facet2}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_gray()
```

## Light

```{r facet3}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_light()
```

## Minimal

```{r facet4}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_minimal()
```

## Dark

```{r facet5}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_dark()
```

## Classic

```{r facet6}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_classic()
```

## Void (Empty)

```{r facet7}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme_void()
```


## Summary

In this post, we learnt about the different themes available in ggplot2.
This brings us to the end of the series **Elegant Data Visualization with ggplot2**.






