---
title: Legend - Part 5
author: ''
date: '2017-09-20'
slug: legend-part-5
topics:
  - data-visualization
tags:
  - ggplot2
  - legend
---

### Introduction

<hr>

If the aesthetics are mapped to variables, ggplot2 automatically creates legends wherever applicable. 
You may want to modify the appearance of legends. In this module, we will learn to modify the legends when
`alpha` is mapped to categorical variables.

Modify legend when `alpha` is mapped to variables. Specifically

- title
- breaks
- limits
- range
- labels
- values
- symbol type

```{r gui1, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
```

<br>

#### Plot

<hr>

```{r leg2, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue')
```

<br>

#### Title

<hr>

```{r leg3, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue') +
  scale_alpha_continuous("Horsepower")
```

<br>

#### Breaks

<hr>

```{r leg4, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue') +
  scale_alpha_continuous(breaks = c(0, 100, 200, 300, 400))
```

<br>

#### Limits

<hr>

```{r leg5, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue') +
  scale_alpha_continuous(limits = c(0, 400))
```

<br>

#### Range

<hr>

```{r leg6, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue') +
  scale_alpha_continuous(range = c(0.4, 0.8))
```

<br>

#### Labels

<hr>

```{r leg7, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue') +
  scale_alpha_continuous(breaks = c(0, 100, 200, 300, 400),
    labels = c("Zero", "Hundred", "2 Hundred", 
      "3 Hundred", "4 Hundred"))
```

<br>

#### Putting it all together

<hr>

```{r leg8, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = hp), color = 'blue') +
  scale_alpha_continuous("Horsepower", breaks = c(0, 100, 200, 300, 400),
    limits = c(0, 400), range = c(0.4, 0.8),
    labels = c("Zero", "Hundred", "2 Hundred", 
      "3 Hundred", "4 Hundred"))
```

<br>

### Alpha - Discrete

<br>

#### Introduction

<hr>

```{r leg9, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = factor(cyl)), color = 'blue')
```

<br>

#### Legend Title

<hr>

```{r leg10, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = factor(cyl)), color = 'blue') +
  scale_alpha_discrete(name = "Cylinders")
```

<br>

#### Legend Breaks

<hr>

```{r leg11, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = factor(cyl)), color = 'blue') +
  scale_alpha_discrete(breaks = c("4", "6", "8"))
```

<br>

#### Legend Range

<hr>

```{r leg12, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = factor(cyl)), color = 'blue') +
  scale_alpha_discrete(range = c(0.4, 0.8))
```

<br>

#### Legend Labels

<hr>

```{r leg13, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = factor(cyl)), color = 'blue') +
  scale_alpha_discrete(labels = c("Four", "Six", "Eight"))
```

<br>

#### Putting it all together

<hr>

```{r leg14, fig.align='center'}
ggplot(mtcars) +
  geom_point(aes(disp, mpg, alpha = factor(cyl)), color = 'blue') +
  scale_alpha_discrete(name = "Cylinders", range = c(0.4, 0.8),
    breaks = c("4", "6", "8"), labels = c("Four", "Six", "Eight"))
```

### Summary

<hr>

<br>

### Up Next..

<hr>

<br>