---
title: Guides - Axes
date: '2017-07-06'
slug: guides-axes
topics:
  - data-visualization
tags:
  - ggplot2
draft: yes
---

# Introduction

Now that we have learnt to build different plots, let us look at different ways to modify the axis. Along the way, we will also explore the `scale_*()` family of functions 

```{r guide1, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
```


- `scale_x_continuous()`: modify x axis when x is continuous

The first function we will explore is `scale_x_continuous()`. It can be used for:

- axis title
- axis labels
- axis limits
- axis breaks
- and axis position

Let us create a simple scatter plot and then use `scale_x_continuous()` to modify the X axis.


```{r guide2}
ggplot(mtcars) +
  geom_point(aes(disp, mpg))
```

```{r guide3}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  scale_x_continuous(name = "Displacement",
                     limits = c(0, 600),
                     breaks = c(0, 150, 300, 450, 600),
                     labels = c('0', '150', '300', '450', '600'),
                     position = 'top')
```

- `scale_y_continuous()`: modify y axis

Now let us modify the Y axis.

```{r guide4}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  scale_y_continuous(name = "Miles Per Gallon",
                     limits = c(0, 45),
                     breaks = c(0, 15, 300, 45),
                     labels = c('0', '15', '30', '45'),
                     position = 'right')
```


Now let us look at plots with discrete X axis.

```{r guide5}
ggplot(mtcars) +
  geom_bar(aes(factor(cyl)))
```

Use `scael_x_discrete()` to modify the X axis.

```{r guide6}
ggplot(mtcars) +
  geom_bar(aes(factor(cyl))) +
  scale_x_discrete(name = "Number of Cylinders",
                   labels = c("4" = "Four", "6" = "Six", "8" = "Eight"),
                   breaks = c("4", "6", "8"),
                   position = "bottom")
```

## Summary

In this post, we learnt how to modify the axis whether it represents a continuous variable or a discrete variable. In the next post, we will learn how to modify the legend when aesthetics are mapped to variables.


