---
title: Working with strings in R using stringr
date: '2017-03-23'
slug: working-with-strings-in-r-using-stringr
topics:
  - data-wrangling
tags:
  - strings
  - stringr
draft: yes
---

# Introduction

This is the eleventh post in the series **Data Wrangling with R**. In the previous [post](https://rsquaredacademy.github.io/blog/post/how-to-work-with-dates-in-r/), we learnt to manipulate date and time using the [lubridate](https://CRAN.R-project.org/package=lubridate) package. In this post, we will learn to work with string data in R using [stringr](http://stringr.tidyverse.org). Let us begin by installing and loading stringr and a set of other pacakges we will be using.

# print
# cat
# paste
# paste0()
# sprintf()

```{r str1, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
library(stringr)
library(tibble)
library(magrittr)
library(purrr)
library(dplyr)
```

As we did in the earlier posts in this series, we will use a case study to explore the various features of the stringr package. You can
download the data for the case study from [here](https://raw.githubusercontent.com/rsquaredacademy/datasets/master/mock_strings.csv) or directly import the data using the readr package. 

```{r import, message=FALSE}
mockstring <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/mock_strings.csv')
mockstring
```

We will do the following in this case study:

- extract domain name from random email ids
- extract image type from url
- extract image dimension from url
- extract extension from domain name
- extract http protocol from url
- extract domain name from url
- extract extension from url
- extract file type from url

### extract domain name from random email ids

```{r str2}
mockstring$email[1:2] %>% 
  str_split(pattern = '@') %>%
  unlist() %>%
  str_subset(pattern = '\\.') %>%
  str_split(pattern = '\\.') %>%
  purrr::map_chr(extract(1))
```

### from image url, extract image type (jpg, png, bmp)

```{r str3}
mockstring$imageurl[1:5] %>%
  str_split(pattern = '\\.') %>%
  purrr::map_chr(extract(3)) %>%
  str_sub(start = 1, end = 3)

mockstring$imageurl[1:5] %>%
  str_split(pattern = '\\.') %>%
  purrr::map_chr(extract(3)) %>%
  str_split(pattern = '/') %>%
  purrr::map_chr(extract(1))
```

### from image url, extract dimension

```{r str4}
pattern <- "[:digits:]"
mockstring$imageurl[1:5] %>%
  str_locate(pattern = "[0-9]") 
  
mockstring$imageurl[1:5] %>%
  str_sub(start = 23) %>%
  str_split(pattern = '\\.') %>%
  purrr::map_chr(extract(1))
```
  
### extract protocol

```{r str6}
mockstring$url[1:5] %>%
  str_split(pattern = '://') %>%
  map_chr(extract(1))
  
k <- mockstring$url[1:5] %>%
  str_locate(pattern = '://') %>%
  data.frame() %>%
  extract2('start') %>%
  subtract(1)

mockstring$url[1:5] %>%
  str_sub(start = 1, end = k)
```

### extract domain name

```{r str7}
n <- mockstring$url[1:5] %>%
  str_locate_all(pattern = "/") %>%
  map_int(extract(3))

mockstring$url[1:5] %>%
  str_sub(end = n) %>%
  str_split(pattern = '\\.') %>%
  map_chr(extract(1)) %>%
  str_sub(start = k + 4)
```

### extract extension

```{r str8}
mockstring$url[1:5] %>%
  str_sub(end = n) %>%
  str_split(pattern = '\\.') %>%
  map_chr(extract(2)) %>%
  str_split(pattern = '/') %>%
  map_chr(extract(1))
```

### extract file type

```{r str9}
# only 2 dots in the url
mockstring$url[1:3] %>%
  str_locate_all(pattern = '\\.') %>%
  map_int(nrow) %>%
  is_greater_than(2) %>%
  sum()
  
# only 1 question mark in the url
mockstring$url[1:3] %>%
  str_locate_all(pattern = "[?]") %>%
  map_int(nrow) %>%
  is_greater_than(1) %>%
  sum()

# location of second dot and 1 question mark
d <- mockstring$url[1:3] %>%
  str_locate_all(pattern = '\\.') %>%
  map_int(extract(2)) %>%
  add(1)

q <- mockstring$url[1:3] %>%
  str_locate_all(pattern = "[?]") %>%
  map_int(extract(1)) %>%
  subtract(1)

mockstring$url[1:3] %>% 
  str_sub(start = d, end = q)
```

## Summary

































