---
title: 'ggplot2: Histogram'
date: '2016-05-06'
slug: ggplot2-histogram
topics:
  - ggplot2
tags:
  - ggplot2
  - visualization
draft: yes
---

# Introduction

This is the eleventh post in the series **Elegant Data Visualization with ggplot2**. In the previous [post](https://rsquaredacademy.github.io/blog/post/ggplot2-box-plots/), we learnt to build box plots. In this post, we will focus on histograms.

```{r hist, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
```

```{r import, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

We will continue to use the ecommerce data. You can download it from [here](https://github.com/rsquaredacademy/datasets/blob/master/web.csv) or import directly using the readr package.

```{r import2, echo=FALSE, eval=FALSE, results='hide', message=FALSE}
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Simple Histogram

```{r hist2}
ggplot(ecom) +
  geom_histogram(aes(n_visit))
```

Let us add some color to the histogram.

```{r hist3}
ggplot(ecom) +
  geom_histogram(aes(n_visit), fill = 'blue')
```

The default number of bins is 30. We can specify the number of bins using `bins`.

```{r hist4}
ggplot(ecom) +
  geom_histogram(aes(n_visit), bins = 7, fill = 'blue', color = 'black')
```

We can specify the width of the bins using `binwidth`.

```{r hist5}
ggplot(ecom) +
  geom_histogram(aes(n_visit), binwidth = 2, fill = 'blue', color = 'black')
```

Line type and size.

```{r hist6}
ggplot(ecom) +
  geom_histogram(aes(n_visit), binwidth = 2, 
                 fill = 'blue', color = 'black', alpha = 0.3,
                 linetype = 2, size = 1.25)
```

We can also map the color to a variable.


```{r hist7}
ggplot(ecom) +
  geom_histogram(aes(n_visit, fill = device), bins = 7)
```


