---
title: A Complete Guide to Importing Data into R - Part 2
date: '2017-07-14'
slug: a-complete-guide-to-importing-data-into-r-part-2
topics:
  - data-wrangling
tags:
  - import
draft: yes
---

# Introduction

This is the fourth post in the series **Data Wrangling with R**. In the previous [post](https://rsquaredacademy.github.io/blog/post/a-complete-guide-to-importing-data-into-r/), we learnt to import data from flat files, excel spreadsheets and statistical softwares. In this post, we will learn to import data from:

- JSON
- XML
- googlesheets

## JSON

A lot of API data is available in the JSON format. You can use the [jsonlite](https://cran.r-project.org/package=jsonlite) package to import JSON data into R.

```{r imp8}
# jsonlite::fromJSON()
```

## XML

Some APIs offer data in the XML format. Use the [xml2](https://cran.r-project.org/package=xml2) package to import XML data into R.

```{r imp9}
# x <- read_xml('sample_xml')

# xml_name(x)
# xml_text(x)
# xml_attrs(x)
# xml_children(x)
# baz <- xml2::xml_find_all(x, './/book')
# xml_path(baz)
# xml_attr(baz, "id")
# xml_structure(x)
# as_list(x)
# 
# library(XML)
# xmlToDataFrame(x, c("character", "character", "character", "numeric", 
#                     "character", "character"))
# 
# cd <- read_xml("http://www.xmlfiles.com/examples/cd_catalog.xml")
```

## HTML

```{r imp10}
# xml2::read_html()
```

## Google Sheets

You can import data from Google Sheets using the [googlesheets]() pacakge.

```{r imp 11}
# mysheets <- gs_ls()
# mysheets %>% glimpse()
# 
# # practice sheets
# gs_gap() %>%
#     gs_copy(to = "Gapminder")
# gs_ls('Gapminder')
# 
# # register sheet
# gap <- gs_title('Gapminder')
# gap
# 
# # get worksheet names
# gs_ws_ls(gap)
# 
# # read data in one worksheet
# oceania <- gap %>%
#     gs_read(ws = "Oceania")
# 
# # read certain cells
# gap %>% gs_read(ws = 2, range = "A1:D8")
```

## Summary