---
title: 'ggplot2: Quick Tour'
date: '2016-02-19'
slug: ggplot2-quick-tour
topics:
  - ggplot2
tags:
  - ggplot2
  - visualization
draft: yes
---

# Introduction

This is the second post in the series **Elegant Data Visualization with ggplot2**. In the previous [post](https://rsquaredacademy.github.io/blog/post/introduction-to-ggplot2/), we understood the concept of grammar of graphics and 
even built a bar plot step by step while exploring the different components of a plot/chart. In this post, we will 
learn to quickly build a set of plots that are routinely used to explore data.

```{r gg1, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
library(ggplot2)
library(dplyr)
```

## Scatter Plot

```{r gg2}
qplot(disp, mpg, data = mtcars)
```

```{r gg3}
qplot(disp, mpg, data = mtcars, geom = c('point', 'line'))
```

```{r gg4}
qplot(disp, mpg, data = mtcars, color = factor(cyl))
```

```{r gg5}
qplot(disp, mpg, data = mtcars, shape = factor(cyl))
```

```{r gg6}
qplot(disp, mpg, data = mtcars, size = qsec)
```

## Bar Plot

```{r gg7}
qplot(factor(cyl), data = mtcars, geom = c('bar'))
```

```{r gg8}
qplot(factor(cyl), data = mtcars, geom = c('bar'), fill = factor(am))
```

## Box Plot

```{r gg9}
qplot(factor(cyl), mpg, data = mtcars, geom = c('boxplot'))
```

```{r gg10}
qplot(factor(1), mpg, data = mtcars, geom = c('boxplot'))
```

```{r gg11}
qplot(factor(cyl), mpg, data = mtcars, geom = c('boxplot', 'jitter'))
```

## Line Chart

```{r gg12}
qplot(x = date, y = unemploy, data = economics, geom = c('line'))
```

```{r gg13}
qplot(x = date, y = unemploy, data = economics, geom = c('line'),
      color = 'red')
```

## Histogram

```{r gg14}
qplot(mpg, data = mtcars, bins = 5)
```

## Summary

In this post, we learnt to quickly create plots using the `qplot()` function. While useful, it has limitations and can be used only to quickly visualize data. In the next [post](https://rsquaredacademy.github.io/blog/post/ggplot2-introduction-to-geoms/), we will create the same set of plots but using **geoms**. 