---
title: 'ggplot2: Statistical Plots'
date: '2016-05-23'
slug: ggplot2-statistical-plots
topics:
  - ggplot2
tags:
  - ggplot2
  - visualization
draft: yes
---

# Introduction

This is the 12th post in the series **Elegant Data Visualization with ggplot2**. In the previous [post](https://rsquaredacademy.github.io/blog/post/ggplot2-histogram/), we learnt to build histograms. In this post, we will explore an alternative method to build plots.

```{r stat, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
```

```{r import, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

We will continue to use the ecommerce data. You can download it from [here](https://github.com/rsquaredacademy/datasets/blob/master/web.csv) or import directly using the readr package.

```{r import2, echo=FALSE, eval=FALSE, results='hide', message=FALSE}
ecom <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/web.csv')
```

## Stats

So far we have used `geom_*()` functions to build plot. Now we will use a new set of functions `stat_*()` to build the plots. 

## Bar Plots

```{r stat2}
ggplot(ecom) +
  stat_count(aes(device))
```

## Box Plots

```{r stat3}
ggplot(ecom) +
  stat_boxplot(aes(factor(1), n_visit))
```

## Scatter Plots

```{r stat4}
ggplot(ecom) +
  stat_identity(aes(n_pages, duration), position = 'jitter')
```

## Histogram

```{r stat5}
ggplot(ecom) +
  stat_bin(aes(n_visit), bins = 7, fill = 'blue', alpha = 0.3,
           color = 'black')
```

## Plot Unique Values

```{r stat6}
ggplot(ecom) +
  stat_unique(aes(n_pages, duration), 
              position = 'jitter')
```

## Summary

In this post, we learnt about the functions underlying the `geom_*()` family of functions. In the next [post](https://rsquaredacademy.github.io/blog/post/ggplot2-facets/), we will learn about faceting i.e. combining plots.

