---
title: Axis & Plot Labels
date: '2017-07-04'
slug: axis-plot-labels
topics:
  - data-visualization
tags:
  - ggplot2
draft: yes
---

# Introduction

This is the fifth post in the series **Elegant Data Visualization with ggplot2**. In the previous [post](https://rsquaredacademy.github.io/blog/post/ggplot2-introduction-to-aesthetics/), we learnt about aesthetics. In this post, we will learn to:

- add title and subtitle to the plot
- modify axis labels
- modify axis range
- remove axis
- format axis

```{r axis1, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
library(ggplot2)
library(dplyr)
library(tidyr)
```

## Basic Plot

Let us start by building a simple scatter plot. 

```{r axis2}
ggplot(mtcars) +
  geom_point(aes(disp, mpg))
```

## Title & Subtitle

You can add a title and subtitle to the plot using the `ggtitle()` function.

```{r axis3}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  ggtitle(label = 'Displacement vs Mileage', subtitle = 'disp vs mpg')
```



## Axis Labels

The axis labels can be modified using the `xlab()` and `ylab()` functions.

```{r axis4}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  xlab('Displacement') + ylab('Miles Per Gallon')
```

We can add all of the above using the `labs()` function as well.

```{r axis5}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  labs(title = 'Displacement vs Mileage',
    subtitle = 'disp vs mpg', x = 'Displacement',
    y = 'Miles Per Gallon')
```

## Axis Range

Sometimes you may want to modify the range of the axis. 

Use the `xlim()` function to modify the range of the X axis.

```{r axis6}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  xlim(c(0, 600))
```

Use the `ylim()` function to modify the range of the Y axis.

```{r axis7}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  ylim(c(0, 40))
```

You can use the `expand_limits()` function as well.

```{r axis8}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  expand_limits(x = c(0, 600), y = c(0, 40))
```

## Remove Axis Labels

If you want to remove the axis labels all together, use the `theme()` function.

```{r axis9}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  theme(axis.title.x = element_blank(),
    axis.title.y = element_blank())
```

What we are doing above is to modify the theme of the plot and set the axis labels to blank using
`element_blank()` function.


## Format Title & Axis Labels

To format the title or the axis labels, we have to modify the theme of the plot using the `theme()` function.
We can modify the color, font family, font face, font size and horizontal position. Let us try them one by one.

The font family can be any of the valid font family types but it must be supported by OS.
The font face can be plain, bold, italic, bold.italic
hjust must be between 0 (extreme left) and 1 (extreme right). 

```{r axis10}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  ggtitle('Diaplacement vs Mileage') +
  theme(plot.title = element_text(color = 'blue',
                                  family = 'Arial',
                                  face = 'bold',
                                  size = 8,
                                  hjust = 0.3))
```

X axis label.

```{r axis11}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  xlab('Diaplacement') +
  theme(axis.title.x = element_text(color = 'blue',
                                  family = 'Arial',
                                  face = 'bold',
                                  size = 8,
                                  hjust = 0.5,
                                  angle = 15))
```


Y axis label.

```{r axis12}
ggplot(mtcars) +
  geom_point(aes(disp, mpg)) +
  ylab('Miles Per Gallon') +
  theme(axis.title.y = element_text(color = 'blue',
                                  family = 'Arial',
                                  face = 'italic',
                                  size = 8,
                                  vjust = 0.3,
                                  angle = 90))
```






















