---
title: How to work with dates in R
date: '2017-03-09'
slug: how-to-work-with-dates-in-r
topics:
  - data-wrangling
tags:
  - lubridate
draft: yes
---

## Introduction

This is the 5th post in the series **Data Wrangling with R**. In the previous [post](https://rsquaredacademy.github.io/post/data-manipulation-in-r-with-dplyr/), we learnt to manipulate dataframes using the [dplyr](https://CRAN.R-project.org/package=dplyr) package. In this post, we will learn to work with date/time data in R using [lubridate]( https://CRAN.R-project.org/package=lubridate), an R package that makes it easy to work with dates and time. Let us begin by installing and loading the lubridate pacakge.

```{r install-lubridate, echo=FALSE}
library(lubridate)
```

### Quick Overview

Use `origin` to get the origin for the `Date` and other date/time objects in R.

```{r origin}
lubridate::origin
```

There are function to check current date, time, timezone and AM/PM. Let us take a quick look at these:

```{r today}
now()
today()
am(now())  
pm(now())
```

In order to explore all the functionality provided by the lubridate package, we will look at a simple scenario. Let us say you are going on a vacation to Atlanta. You plan to reach there on 10th April 2017 and end your vacation on 18th April 2017. Let us save these dates as *arrival* and *departure*.


