---
title: Why you should purrr?
date: '2017-06-23'
slug: why-you-should-purrr-part-1
topics:
  - data-wrangling
tags:
  - purrr
draft: yes
---

This is the 10th post in the series **Data Wrangling with R**. In the previous [post](https://rsquaredacademy.github.io/blog/post/data-manipulation-in-r-with-dplyr-part-3/), we learnt helper functions in [dplyr](http://stringr.tidyverse.org) package. In this post, we will learn about [purrr](http://purrr.tidyverse.org), an R package that enhances R's functional programming toolkit. Let us begin by installing and loading purrr and a set of other pacakges we will be using.


```{r str1, echo=FALSE, eval=TRUE, results='hide', message=FALSE}
library(tibble)
library(magrittr)
library(purrr)
library(dplyr)
```

As we did in the earlier posts in this series, we will use a case study to explore the various features of the stringr package. You can
download the data for the case study from [here](https://raw.githubusercontent.com/rsquaredacademy/datasets/master/mock_strings.csv) or directly import the data using the readr package. 

```{r import, message=FALSE}
mockstring <- readr::read_csv('https://raw.githubusercontent.com/rsquaredacademy/datasets/master/mock_strings.csv')
mockstring
```

We will do the following in this case study:

- extract domain name from random email ids
- extract image type from url
- extract image dimension from url
- extract extension from domain name
- extract http protocol from url
- extract domain name from url
- extract extension from url
- extract file type from url
